On proving things

### 2015-10-17 reasoning/huiswerk/inl1019.tex
finished 3??

\documentclass{article}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

@@

The only applicable rules left in GKC are the $L\wedge$ and $R\vee$ rules.
Both the $L\wedge$ and $R\vee$ rules add only 1 connective to the conclusion
once applied to the premise, creating a new sequent in the process. The proof
of $S$ also has just a single branch, because $L\wedge$ and $R\vee$ only allow
a single premise.
So the
sequent count in the proof of $S$ is at least $n$. It is $n$ + 1 because $S$ is also
a sequent by definition. This is what had to be shown.
\end{document}

>>>>

\documentclass{article}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

Everywhere where postive is used negative can also be used as long
that everywhere where negative is used is replaced by positive.

@@

The only applicable rules left in GKC are the $L\wedge$ and $R\vee$ rules.
Both the $L\wedge$ and $R\vee$ rules add only 1 connective to the conclusion
once applied to the premise, creating a new sequent in the process. The proof
of $S$ also has just a single branch, because $L\wedge$ and $R\vee$ only allow
a single premise.
So the
sequent count in the proof of $S$ is at least $n$. It is $n$ + 1 because $S$ is also
a sequent by definition. This is what had to be shown.
\section{Proof of $GK_{\{\neg, \wedge\}}$ is complete}
Let $GK_{\{\neg, \wedge\}}$ be the calcules consisting of the axiom
$(\Gamma, A \Rightarrow A, \Delta)$ where $A$ is an atom, and the rules:

\begin{prooftree}
	\AxiomC{$\Gamma \Rightarrow A, \Delta$}
	\RightLabel{$L\neg$}
	\UnaryInfC{$\Gamma, \neg A \Rightarrow \Delta$}
\end{prooftree}
\begin{prooftree}
	\AxiomC{$\Gamma, A \Rightarrow \Delta$}
	\RightLabel{$R\neg$}
	\UnaryInfC{$\Gamma \Rightarrow \neg A, \Delta$}
\end{prooftree}

\begin{prooftree}
	\AxiomC{$\Gamma, A, B \Rightarrow \Delta$}
	\RightLabel{$L\wedge$}
	\UnaryInfC{$\Gamma, A \wedge B \Rightarrow \Delta$}
\end{prooftree}

\begin{prooftree}
	\AxiomC{$\Gamma \Rightarrow A, \Delta$}
	\AxiomC{$\Gamma, \Rightarrow B, \Delta$}
	\RightLabel{$R\wedge$}
	\BinaryInfC{$\Gamma \Rightarrow A \wedge B, \Delta$}
\end{prooftree}
To prove that $GK_{\{\neg, \wedge\}}$ is complete with respect to
$CPC_{\{\neg, \wedge\}}$.

The completness of $GK_{\{\neg, \wedge\}}$ can be proven by showing
that If $\nvdash S$, then $v(I(S)) = 0$

$\Gamma \cup \Delta$  consists of atoms and $\Gamma \cap \Delta \not= \o$

Valuation $v(p) = 1$  if $p \in \Gamma$ and $v(p) = 0$ if $p \in \Delta$

$S$ should not be derivable, so there is a leaf that is not an axiom.
This means $V(I(l)) = 0$ where l is the leaf.

If the valuation of the premise is 0, then so is the conclusion for any of
the rules in $GK_{\{\neg, \wedge\}}$. This is shown in 2.1.

So $V(I(S))$ is also 0 because one of the leafs is 0, which eventually
will find its way to the final conclusion.

\end{document}
